

```{r setup, include=FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

* * *

## Lab report - William Marcus, Joy Reeves, Gio, Emma

#### Load data:
```{r}
load(url("https://stat.duke.edu/~mc301/data/nycflights.RData"))
names(nycflights)
str(nycflights)
```

#### Exercise 1: 
They have different x limits 


```{r ex1}
qplot(x = dep_delay, data = nycflights, geom = "histogram")

qplot(x = dep_delay, data = nycflights, geom = "histogram", binwidth = 15)
qplot(x = dep_delay, data = nycflights, geom = "histogram", binwidth = 150)
      
rdu_flights <- nycflights %>%
  filter(dest == "RDU")
qplot(x = dep_delay, data = rdu_flights, geom = "histogram")


rdu_flights %>%
  summarise(mean_dd = mean(dep_delay), sd_dd = sd(dep_delay), n = n())
```

#### Exercise 2: 


68
```{r ex2}
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)


```

#### Exercise 3: 



```{r ex3}
qplot(x = arr_delay, data = sfo_feb_flights, geom = "histogram")

sfo_feb_flights %>%
  summarise(mean_dd = mean(arr_delay), sd_dd = sd(arr_delay), n = n())
```

#### Exercise 4: 


Total Median is -11
Total IQR is 23.25

EQR Median is -15.5
JFK Median is -10.5

EWR IQR is 17.5
JFK IQR is 22.75

JFK has more variable arrival delays
```{r ex4}
sfo_feb_flights %>%

  summarise(median_sfo_febflight = median(arr_delay), iqr_sfo_febflight = IQR(arr_delay), n = n())
sfo_feb_flights %>%
  group_by(origin) %>%
  summarise(median_sfo_febflight = median(arr_delay), iqr_sfo_febflight = IQR(arr_delay), n = n())

```

#### Exercise 5: 

LGA has the highest on time departure rate

```{r ex5}
qplot(y = dep_delay, x = factor(month), data = nycflights, geom = "boxplot")

nycflights <- nycflights %>%
  mutate(dep_type = ifelse(dep_delay < 5, "on time", "delayed"))

nycflights %>%
  group_by(origin) %>%
  summarise(ot_dep_rate = sum(dep_type == "on time") / n()) %>%
  arrange(desc(ot_dep_rate))

```

#### Exercise 6: 

LGA has the highest departure percentage

```{r ex6}
qplot(x = origin, fill = dep_type, data = nycflights, geom = "bar")

```


* * *

### On your own:

#### 1:



```{r oyo1}
nycflights <- nycflights %>%
  mutate(avg_speed = (distance/(air_time/60)))
```

#### 2:

N666DN

```{r oyo2}
nycflights %>%
  arrange(desc(avg_speed))

```

#### 3:



```{r oyo3}
qplot(x = distance, y = avg_speed, data = nycflights, geom = "point", color = I("blue"))

```

#### 4:


On time arrival rate was .776 for on time departures and was .18 for delayed departures.
```{r oyo4}
nycflights <- nycflights %>%
  mutate(arr_type = ifelse(arr_delay <= 0, "on time", "delayed"))

nycflights %>%
  group_by(dep_type) %>%
  summarise(ot_arr_rate = sum(arr_type == "on time") / n()) %>%
  arrange(desc(ot_arr_rate))

```

#### 5:



```{r oyo5}
list_ <- c("AA", "DL", "UA")

ans_flights <- filter(nycflights, carrier %in% list_)


qplot(x = dep_delay, y = arr_delay, data = ans_flights, geom = "point", xlim = c(0,850), ylim = c(0,850), color = carrier)

```
